---
title: "Nero vom Buchonia Offspring Data"
subtitle: ""
excerpt: "The Nero vom Buchonia dataset contains show ratings, performance titles, and health information about the offspring of a male workingline German Shepherd Dog named G Nero vom Buchonia IGP3 KKL."
date: "2024-03-18"
author: "Laura Briggs"
draft: false
images:
series:
tags:
categories:
  - workshop
  - data cleaning
  - diagram
  - R script
  - R Studio
  - Canva
  - data analysis
  - GSD data
  - active learning
layout: single
---

```{r include=FALSE}

#list of required packages
pkg2 <- c("gt", "tidyverse", "gtExtras", "here")

#install and load packages that are not already installed

#we use a for loop to automate the process of checking, installing,
#and loading each package in our list, saving time and avoiding manual repetition
#where 'p' represents the current package name being processed in each iteration of the loop

for (p in pkg2) {  #iterate over each package name in the pkg2 vector
  if (!require(p, character.only = TRUE, quietly = FALSE)) {  #check if the package is installed
    install.packages(p)  #install the package if it is not installed
  }
  library(p, character.only = TRUE, quietly = FALSE)  #load the package after installation
}

```

### Description Of The Dataset

The Nero vom Buchonia dataset contains show ratings, performance titles, and health information about the offspring of a male workingline German Shepherd Dog named G Nero vom Buchonia IGP3 KKL.
It represents a typical dataset observed in the context of German Shepherd Dog (GSD) breeding.

Note that the dataset:

* Uses specialized terminology that might be unfamiliar to you.
* There are missing values in the dataset. 
* The information is derived from a mixture of public and private data    sources.

### It's Important To Note

The table below is only a small subset of a much larger dataset. 
No data dictionary is available, a common feature of canine datasets.
For educational purposes, web scraping is permitted in order to access the data for analysis.

### Acknowledgement

Thank you to Jennifer Lee, Nero's owner, for helping to create this dataset for the workshop.

### The Dataset

```{r Offspring Data, include=FALSE}

#create the dataframe for the Nero vom Buchonia offspring data

nero_data <- data.frame("Name" = c("G Nero vom Buchonia IGP3", "Faine Auf der Marquis IGP1", "Falco Auf der Marquis IGP1", "Forest Ranger Auf der Marquis IGP1", "Fallon Auf der Marquis IGP1", "Yogi vom Owenberg", "SG Brynn vom Adlerland IGP2", "Banshee vom Aderland ACT2", "Baha vom Aderland CGC", "Baalos vom Aderland", "Tesla vom Wildhaus IGP1", "Trauma vom Wildhaus IGP1", "Torque vom Wildhaus", "Chimera von Bairdhaus", "SG Halo z Tammik BH", "Blackthorn's Game Changer", "G Kikki von Bairdhaus IGP3"),
  "KKL" = c("Yes","", "", "", "", "", "", "", "", "","", "", "", "", "", "", "Yes"),
  "BirthDate" = c("March 9, 2013", "May 10, 2019", "May 10, 2019", "May 10, 2019", "May 10, 2019", "May 10, 2019", "August 28, 2018", "August 28, 2018", "August 28, 2018", "August 28, 2018", "January 13, 2018", "January 13, 2018", "January 13, 2018", "January 13, 2018", "September 15, 2020", "November 20, 2020", "December 20, 2020"),
  "Sex" = c("Male", "Male", "Male", "Male", "Female", "Male", "Female", "Female", "Female", "Male", "Female", "Female", "Male", "Female", "Male", "Male", "Female"),
  "Colour" = c("grey", "black-tan", "grey", "grey", "bicolor", "black-tan", "sable", "bicolor", "black-tan", "black-tan", "black-tan", "sable", "bicolor", "grey", "black-tan", "sable", "grau"),
"HipsAndElbowsRating" = c("a-normal; Normal", "a-normal; Normal", "a-normal; Normal", "a-normal; Normal", "a-normal; Normal", "a-normal; Fast Normal", "Excellent; Normal", "Good; Normal", "Good; Normal", "Good; Normal", "a-normal; Normal", "Excellent; Normal", "NA; Normal", "Mittlere; Normal", "a-normal; Normal", "Good; Normal", "a-fast normal; Fast Normal"),
"ZW" = c(88, 80, 80, 80, 80, 80, "", "", "", "",80, "", "", 120, 80, "", 99)
)
                        
```

```{r Output Table, echo=FALSE}

#create a display table using the gt library

nero_data %>%
  gt() %>%
  #apply the fancy NT TImes theme
  gtExtras::gt_theme_nytimes() %>%
  #center the data in the columns except the first column
    cols_align(
      align = "center",
      columns =  c(2:7)
    ) %>%
    #prevent the cells from breaking at hyphens
    text_transform(
    locations = cells_body(),  #apply to body cells
    fn = function(x) gsub("-", "\u2011", x)  #replace hyphens with non-breaking hyphens
    ) %>%
    #add a title
    tab_header(
      title = md("**Nero vom Buchonia Offspring Data**")
      ) %>%
    #bold and format the column names
    cols_label(
      Name = md("**Name**"),
      KKL = md("**KKL**"),
      BirthDate = md("**Birth Date**"),
      Sex = md("**Sex**"),
      Colour = md("**Colour**"),
      HipsAndElbowsRating = md("**Hips And Elbows Rating**"),
      ZW = md("**ZW**")
    ) %>%
    #add HTML code to center the content in the cells
    tab_style(
      style = list(
      cell_text(align = "center") #center align text in cells
    ),
    #apply styling to table body cells in columns 2 to 7 cells
      locations = cells_body(columns = c(2:7))
  ) %>%
   #add HTML code to center the content in the cells of the header
    tab_style(
    style = list(
      cell_text(align = "center")
    ),
    locations = cells_stub() #apply the HTML code to center the content in the cells of the header
  ) 

```
